Using GLMs to Predict Basketball Games

### 2021-04-23 paper/paper.Rmd
final paper

Every year qualifying Division I basketball teams compete in the annual March Madness tournament. Casual fans and enthusiasts submit predictions gambling small sums of money in hopes of completing a perfect bracket. A perfect bracket is when one correctly predicts the outcome of all 63 games. This study uses logistic, poisson, and multinomial regression models fitted with R [@R-base] to predict the outcomes of the March Madness tournament  games^[Rcripts and datasets assocaited with this project can be found in this [Github Repository](https://github.com/despresj/March-Madness)]. Our primary objective is to determine which of these GLMs make the most accurate predictions. To begin, we collect data from three different sources Kaggle [@R-Kaggle], NCAA [@R-NCAA], and the tournament results [@R-NCAA]. Kaggle [@R-Kaggle], provides a comprehensive dataset including all NCAA in-season basketball games from 2001 to 2020. The NCAA [@R-NCAA] provides team-level statistics for each team. We filter, clean, and combine these data using the tidyverse package [@R-tidyverse]. Then use the combination of these datasets to fit our models. The objective is to predict the individual game outcomes as accurately as possible and determine which GLM is the most accurate.  

>>>>

Every year qualifying Division I basketball teams compete in the annual March Madness tournament. Casual fans and enthusiasts submit predictions gambling small sums of money in hopes of completing a perfect bracket. A perfect bracket is when one correctly predicts the outcome of all 63 games. This study uses logistic, poisson, and multinomial regression models fitted with R [@R-base] to predict the outcomes of the March Madness tournament  games^[Scripts and datasets assocaited with this project are published in this [Github Repository](https://github.com/despresj/March-Madness)]. Our primary objective is to determine which of these GLMs make the most accurate predictions. To begin, we collect data from three different sources Kaggle [@R-Kaggle], NCAA [@R-NCAA], and the tournament results [@R-NCAA]. Kaggle [@R-Kaggle], provides a comprehensive dataset including all NCAA in-season basketball games from 2001 to 2020. The NCAA [@R-NCAA] provides team-level statistics for each team. We filter, clean, and combine these data using the tidyverse package [@R-tidyverse]. Then use the combination of these datasets to fit our models. The objective is to predict the individual game outcomes as accurately as possible and determine which GLM is the most accurate.  

### 2021-04-23 paper/paper.tex
final paper

Every year qualifying Division I basketball teams compete in the annual March Madness tournament. Casual fans and enthusiasts submit predictions gambling small sums of money in hopes of completing a perfect bracket. A perfect bracket is when one correctly predicts the outcome of all 63 games. This study uses logistic, poisson, and multinomial regression models fitted with R (R Core Team, 2020) to predict the outcomes of the March Madness tournament games\footnote{Rcripts and datasets assocaited with this project can be found in this \href{https://github.com/despresj/March-Madness}{Github Repository}}. Our primary objective is to determine which of these GLMs make the most accurate predictions. To begin, we collect data from three different sources Kaggle (Kaggle, 2021), NCAA (NCAA, 2021), and the tournament results (NCAA, 2021). Kaggle (Kaggle, 2021), provides a comprehensive dataset including all NCAA in-season basketball games from 2001 to 2020. The NCAA (NCAA, 2021) provides team-level statistics for each team. We filter, clean, and combine these data using the tidyverse package (Wickham et al., 2019). Then use the combination of these datasets to fit our models. The objective is to predict the individual game outcomes as accurately as possible and determine which GLM is the most accurate.\\

>>>>

Every year qualifying Division I basketball teams compete in the annual March Madness tournament. Casual fans and enthusiasts submit predictions gambling small sums of money in hopes of completing a perfect bracket. A perfect bracket is when one correctly predicts the outcome of all 63 games. This study uses logistic, poisson, and multinomial regression models fitted with R (R Core Team, 2020) to predict the outcomes of the March Madness tournament games\footnote{Scripts and datasets assocaited with this project are published in this \href{https://github.com/despresj/March-Madness}{Github Repository}}. Our primary objective is to determine which of these GLMs make the most accurate predictions. To begin, we collect data from three different sources Kaggle (Kaggle, 2021), NCAA (NCAA, 2021), and the tournament results (NCAA, 2021). Kaggle (Kaggle, 2021), provides a comprehensive dataset including all NCAA in-season basketball games from 2001 to 2020. The NCAA (NCAA, 2021) provides team-level statistics for each team. We filter, clean, and combine these data using the tidyverse package (Wickham et al., 2019). Then use the combination of these datasets to fit our models. The objective is to predict the individual game outcomes as accurately as possible and determine which GLM is the most accurate.\\
